---
title: "Introduction to Package binomial"
author: "Andrew Vuong"
date: "5/1/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Package binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Package

The package `"binomial"` is a minimal implementation for calculating probabilities of a Binomial random variable and related calculations such as the probability distribution, the expected value, variance, and more.

## Calculating Combinations

You can use the function `bin_choose()` to calculate the number of combinations in which k successes can occur in n trials:

```{r, fig.show='hold'}
bin_choose(n = 5, k = 2)
```

## Calculating Probabilities

You can use the function `bin_probability()` to calculate the probability or probabilities of getting k successes in in n trials while assuming a p probability of success. You can have a vector of multiple success values as well.

```{r, fig.show='hold'}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:3, trials = 5, prob = 0.5)
```


## Getting the Binomial Probability Distribution

You can use the function `bin_distribution()` to create a `"bindis"` object that is a data frame of the binomial probability distribution. The first column will contain the succeses and the second column will contain probability.

```{r, fig.show='hold'}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
```

The `plot.bindis()` method gives you a nice barplot graph to display the probability histogram of the binomial distribution object `"bindis"`:
```{r, fig.show='hold'}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Getting the Binomial Cumulative Distribution

You can use the function `bin_cumulative()` to create a `"bincum"` object that is a data frame of the binomial cumulative distribution. The first column will contain the succeses and the second column will contain probability and the third column will contain the cumulative probabilities.

```{r, fig.show='hold'}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
```

The `plot.bincum()` method gives you a nice line graph to display the cumulative distribution of the binomial distribution object `"bincum"`:
```{r, fig.show='hold'}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


## Creating a Binomial Random Variable

You can use the function `bin_variable()` to create a `"binvar"` object that is a binomial random variable containing a list of number of trials,and probability of success.

```{r, fig.show='hold'}
bin1 <- bin_variable(trials = 10, prob = 0.3)
```

The `print.binvar()` method gives you the nicely printed contents of the binomial random variable `"binvar"` object:
```{r, fig.show='hold'}
bin1 <- bin_variable(trials = 10, prob = 0.3)
bin1
```

The `summary.binvar()` method takes an object `"binvar"` and gives you a list of class `"summary.binvar"` containing named elements: number of trials, probability of success, mean, variance, mode, skewness, and kurtosis:
```{r, fig.show='hold'}
bin1 <- bin_variable(trials = 10, prob = 0.3)
binsum1 <- summary(bin1)
```

The `print.summary.binvar()` method gives you the nicely printed contents of the list `"summary.binvar"` object:
```{r, fig.show='hold'}
bin1 <- bin_variable(trials = 10, prob = 0.3)
binsum1 <- summary(bin1)
binsum1
```

## Using Functions of Measures

This package also contains main functions for calculating various measurements of the binomial including the mean, variance, mode, skewness, and kurtosis. All of these arguments will take the two arguments trials and probability:

```{r, fig.show='hold'}
bin_mean(n = 10, p = 0.3)
bin_variance(n = 10, p = 0.3)
bin_mode(n = 10, p = 0.3)
bin_skewness(n = 10, p = 0.3)
bin_kurtosis(n = 10, p = 0.3)
```
